---
title: "Illustrating the Multimodal Marginal Epistasis Test with Simulated Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Illustrating the Multimodal Marginal Epistasis Test with Simulated Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mmer)
```

Use the convenient function that estimates memory requirements based on input parameters. You can use this function to either estimate the memory for the settings you are planning to run or to find parameters that can be run given your memory constraints. In particular the parameters `n_blocks`, `n_randvecs`, and `chunksize` can be chosen freely. Both `chunksize` but particularly `n_randvecs` have an impact on the accuracy of the estimates.

```{r memory}
n_samples <- 300000
n_snps <- 1000000
n_blocks <- 100
n_randvecs <- 100
chunksize <- 100
estimated_memory <- approximate_memory_requirements(n_samples, n_snps, n_blocks, n_randvecs, chunksize)

print(sprintf("Estimated memory requirements: %.2f GB", estimated_memory))
```


